---
title: "clv_calculator"
output: html_document
date: "2023-03-15"
Code by: Matheus Leal Leone - TI1014894
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## About CLV

Customer lifetime value (CLV) is a business metric that measures how much a business can plan to earn from the average customer over the course of the relationship.

It's possible to calculate the CLV by knowing the average revenue per costumer (a typical customer is a person that shops regularly) and the average lifetime of a costumer.

## Challenge

As a Tim Horton's costumer, I started drinking coffee since January 2020. In average, I spend \$6.45 per visit, 3 times during the week until now. Now, I have to calculate my CLV.

## About the solution

As told before, I spend, on average, \$6.45 per visit, 3 times per week, which give us a total of \$19.35 per week. Considering that 1 month has (on average) 4 weeks, I spend \$77.4 per full month. I built a simple CSV file to be our guide for this calculation.

## Creating the DataFrame

```{r}
df = data.frame(read.csv("coffe_data.csv", sep = ";"))
df
```

## CLV Formula

Now that we have our DataFrame, we need to calculate de CLV. For that, we'll need to calculate my average annual cost and my lifetime as a costumer. Since I started to be a Tim Horton's costumer in January 2020, my total time in years, until now, is around 3.3 years (2020, 2021, 2023 and 3.5 months).

```{r}
average_cost <- sum(df$cost)
total_time <- 3.3

average_cost
```

## My CLV

With all values required, we just need to calculate my CLV.

```{r}
clv <- average_cost * total_time
cat("My Costumer Lifetime Value is $", clv)
```

## Increasing the profit margin

Following the instructions, let's see what happens to the CLV if we increase the profit margin by 25%.

```{r}
new_average_cost <- average_cost * 1.25
new_average_cost
```

```{r}
clv <- new_average_cost * total_time
cat("My new Costumer Lifetime Value is $", clv)
```

## Another customer example

Now, let's evaluate the CLV for a customer that spends more than \$2000 in a period of two years. For that, I'm going to use a CSV file available on GitHub (customer_eval) to find someone who fits our requirements.

```{r}
new_df <- data.frame(read.csv("customer_eval.csv"))
new_df
```

By taking a look in this new DataFrame, we can't see clearly how many clients did spend more than \$2000. We can create a filter to find out which one of this is OK with our requirements. First, I'll create a matrix with unique values.

```{r}
unique_id <- matrix(unique(new_df$CustomerID), 7)
unique_id
```

With a loop, it's possible to filter each of these values to see if they match what we need.

```{r}
for (i in unique_id){
  customer_df <- new_df[new_df$CustomerID == i,]
  customer_df <- na.omit(customer_df)
  ifelse(sum(customer_df$Quantity * customer_df$UnitPrice) >= 2000, print(i), next)
}

```

Now that we know that customers "16029" and "16210" did spend more than \$2000, we can proceed.

```{r}
customer_df <- new_df[new_df$CustomerID == 16210,]
customer_df <- na.omit(customer_df)
customer_df

```

Now we just need to sum the values.

```{r}
total_cost <- sum(customer_df$Quantity * customer_df$UnitPrice)
total_cost
```

## CLV

The dataset is showing us that this client spent the total_cost value (above) in one day. For study purposes and to fulfill what has been asked in the exercise, let's pretend that this customer spent this value in 2.5 years.

The CLV for the customer that holds the ID 16210 would be:

```{r}
clv <- total_cost * 2.5
cat("CLIENT ID 16210 CLV's: $", clv)
```
